---
title: "project_test"
output: html_document
date: "2023-12-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Preliminary Analysis 
```{r}
setwd("/Users/sawal/Documents/stanford_ms_icme/courses/autumn_23/stats209/project")
library(haven)
library(dplyr)
library(tidyr)
library(ggplot2)
library(estimatr)
library(stargazer)
library(broom)
library(panelr)
library(margins)
library(betareg)
library(synthdid)
library(ggplot2)
library(data.table)
library(xtable)
```
#### Generating data for Incident Types Plot 
```{r}
main_df <- read_dta("clean_parliament_data.dta")
casualty_df<- read_dta("casualty_info/casualty_data_joshi")
casualty_df_sub <- na.omit(select(casualty_df, Year, IncidentOutcome, 
                                    IncidentDistrict))
casualty_df_sub$OutcomeDescription <- "Killed"
casualty_df_sub$OutcomeDescription[casualty_df_sub$IncidentOutcome == 3] <- "Injured"
casualty_df_sub$OutcomeDescription[casualty_df_sub$IncidentOutcome == 2] <- "Disappeared"
```

#### Plot of Incident Types 
```{r}
plot <- ggplot(casualty_df_sub, aes(x=as.factor(Year), fill=OutcomeDescription)) +     
  geom_bar() + 
  theme(axis.text.x = element_text(angle = 90, size = 10)) + 
  labs(y="Victim Count", x="Year") +
  guides(fill=guide_legend(title="Incident Type"))
ggsave("incident_barplot.pdf", plot, width=11, height=6)
```

#### Plot for victim count by conflict intensity
```{r}
subset_2008 <- subset(main_df, year==2008)
subset_2008$conflict_intensity <- "High"
subset_2008$conflict_intensity[subset_2008$high_conflict_gov == 0] <- "Low"
plot <- ggplot(data=subset_2008, aes(x=as.factor(District), y=vic_cn, fill=factor(conflict_intensity))) + geom_bar(stat="identity") +
   theme_bw() + labs(y="Victim Count", x="District")+
  theme(axis.text.x = element_text(angle = 90, size = 7.5))+
  guides(fill=guide_legend(title="Conflict Intensity"))
ggsave("conflict_barplot_distict.pdf", plot, width=11, height=6)
 
subset_agg <- aggregate(vic_cn ~ high_conflict_gov, data=subset_2008, sum)
subset_agg$intensity <- "High"
subset_agg$intensity[subset_agg$high_conflict_gov == 0] <- "Low"
plot_2 <- ggplot(data=subset_agg, aes(x=intensity, y=vic_cn)) + geom_bar(stat="identity", width=0.5) + 
  labs(y="Victim Count", x="Conflict Intensity") + geom_col(width = 0.1)
ggsave("conflict_intensity.pdf", plot_2, width=7, height=6)
```

#### Parallel Trend Plot 

```{r}
data_voter <- main_df[c("District", "year", "turnout_vage", "high_conflict_gov")]
high_district <- unique(data_voter$District[data_voter$high_conflict_gov==1])
data_voter$all_high <- as.numeric(data_voter$District  %in% high_district)
test_agg_high <- aggregate(turnout_vage~year+all_high, data=data_voter, 
                           mean, na.action = NULL, na.rm=FALSE)
test_agg_high$intensity <- "high"
test_agg_high$intensity[test_agg_high$all_high == 0] <- "low"

line_plot <- ggplot(data=test_agg_high, aes(x=as.factor(year), y=turnout_vage, group=intensity)) +
  geom_line(aes(color=intensity)) + geom_point() + 
  labs(y="Voter Turnout Rate", x="Year") + 
  guides(color = guide_legend(title = "Conflict Intensity"))

ggsave("parallel_trend.pdf",line_plot, width=7, height=4)
```
#### Running Baseline Difference in Difference 
$$Y_{it} = \alpha + \beta D_i^{\text{HighConflict}} + \gamma T_t^{\text{Post}} + \delta \left(D_i^{\text{HighConflict}} \times T_t^{\text{Post}} \right) + \epsilon_{it} $$
```{r}
did_data <- main_df[c("District", "year", "turnout_vage", "high_conflict_gov")]
did_data$turnout_vage[did_data$turnout_vage>100] <- 100
did_data$turnout_rate <- did_data$turnout_vage / 100

did_data$treated <- as.numeric(did_data$District  %in% high_district)
did_data$post <- ifelse(did_data$year>2000, 1, 0)
did_data$interaction <- did_data$treated * did_data$post
did_data_sub <- subset(did_data, did_data$year < 2010  )
did_regression <- lm(turnout_rate ~ post + treated + interaction, data=did_data_sub)
summary(did_regression)
table_output <- xtable(did_regression)
print(table_output)
#tidy(summary(did_regression)) ->did_regression

#stargazer(did_regression, type='latex', summary=FALSE)
```
#### Placebo Test 
We set 1996 as the treatment year and see that happens. 
```{r}
did_placebo <- main_df[c("District", "year", "turnout_vage", "high_conflict_gov")]
did_placebo$turnout_vage[did_placebo$turnout_vage>100] <- 100
did_placebo$turnout_rate <- did_placebo$turnout_vage / 100

did_placebo$treated <- as.numeric(did_placebo$District  %in% high_district)
did_placebo$post <- ifelse(did_placebo$year>1996, 1, 0)
did_placebo$interaction <- did_placebo$treated * did_placebo$post
did_sub_placebo <- subset(did_placebo, did_placebo$year<2000)
did_reg_placebo <- lm(turnout_rate ~ post + treated + interaction, data=did_sub_placebo)
table_placebo <- xtable(did_reg_placebo)
print(table_placebo)
```

#### Adding covariate to the data 
```{r}
literacy_data <- read.csv("literacy_pooled_data.csv", check.names = FALSE)
#literacy_panel <- panel_data(literacy_data, id=District, wave=)
did_data_covar <- merge(did_data, literacy_data, by=c("year", "District"))
did_data_covar$literacy_rate <- did_data_covar$literacy_rate / 100
```

#### Difference in Differences with Covariates
```{r}
did_regression_covar <- lm(turnout_rate ~ post + treated + interaction + literacy_rate, 
                           data=did_data_covar)
summary(did_regression_covar)
table <- xtable(did_regression_covar)
print(table)
```

#### Beta Regression 
```{r}
did_data$turnout_rate[did_data$turnout_rate ==1] <-0.99
beta_reg <- betareg(turnout_rate ~ post + treated + interaction, data=did_data)
summary(beta_reg)
#table_beta <- xtable(summary(beta_reg))
#print(table_beta)
beta_m <- margins(beta_reg)
summary(beta_m)
```

#### Looking at Election Counts
```{r}
data_election <- main_df[c("District", "year", "elec91_vote_cast", "elec94_vote_cast", 
                           "elec99_vote_cast", "elec08_vote_cast", "elec13_vote_cast", "high_conflict_gov")]
data_election <- data_election %>% mutate(votes = coalesce(elec91_vote_cast, elec94_vote_cast, 
                           elec99_vote_cast, elec08_vote_cast, elec13_vote_cast)) 
data_election$all_high <- as.numeric(data_election$District  %in% high_district)
data_election <- data_election[c("District", "year", "votes", "all_high")]
agg_election <- aggregate(votes~year+all_high, data=data_election, 
                           mean, na.action = NULL, na.rm=FALSE)
agg_election$intensity <- "high"
agg_election$intensity[agg_election$all_high == 0] <- "low"

line_plot <- ggplot(data=agg_election, aes(x=as.factor(year), y=votes, group=intensity)) +
  geom_line(aes(color=intensity)) + geom_point() + 
  labs(y="Total Votes", x="Year") + 
  guides(color = guide_legend(title = "Conflict Intensity"))
line_plot 
```

#### Compiling population statistics 
```{r}
data_population <- main_df[c("District", "year", "elec91_RegisteredVoters", "elec94_RegisteredVoters",
                             "elec99_RegisteredVoters", "elec08_RegisteredVoters", 
                             "elec13_RegisteredVoters")]
data_population <- data_population %>% mutate(population = coalesce(elec91_RegisteredVoters, elec94_RegisteredVoters, 
                           elec99_RegisteredVoters, elec08_RegisteredVoters, elec13_RegisteredVoters)) 
data_population <- data_population[c("District", "year", "population")]
data_pop_vote <- merge(data_population, data_election, by=c("year", "District"))
data_pop_vote$treated <- as.numeric(data_pop_vote$District  %in% high_district)
data_pop_vote$post <- ifelse(data_pop_vote$year>2000, 1, 0)
data_pop_vote$interaction <- data_pop_vote$treated * data_pop_vote$post
```

#### GLM with poisson model 
```{r}
poisson.model <- glm(votes ~ treated + post +interaction + population , data=data_pop_vote, 
                     family = poisson(link = "log"))
lm_model <- lm(votes ~ treated + post +interaction + population, data =data_pop_vote)
#summary(poisson.model)
coef(lm_model)
```

```{r}
panel.matrices.test = function(panel, unit = 1, time = 2, outcome = 3, treatment = 4, treated.last = TRUE) {
  # TODO: add support for covariates X, i.e. could keep all other columns
  keep = c(unit, time, outcome, treatment)
  if (!all(keep %in% 1:ncol(panel) | keep %in% colnames(panel))) {
    stop("Column identifiers should be either integer or column names in `panel`.")
  }
  index.to.name = function(x) { if(x %in% 1:ncol(panel)) { colnames(panel)[x] } else { x } }
  unit = index.to.name(unit)
  time = index.to.name(time)
  outcome = index.to.name(outcome)
  treatment = index.to.name(treatment)
  keep = c(unit, time, outcome, treatment)

  panel = panel[keep]
  if (!is.data.frame(panel)){
    stop("Unsupported input type `panel.`")
  }
  if (anyNA(panel)) {
    stop("Missing values in `panel`.")
  }
  if (length(unique(panel[, treatment])) == 1) {
    print(panel[, treatment])
    stop("There is no variation in treatment status.")
  }
  if (!all(panel[, treatment] %in% c(0, 1))) {
    stop("The treatment status should be in 0 or 1.")
  }
  # Convert potential factor/date columns to character
  panel = data.frame(
    lapply(panel, function(col) {if (is.factor(col) || inherits(col, "Date")) as.character(col) else col}), stringsAsFactors = FALSE
  )
  val <- as.vector(table(panel[, unit], panel[, time]))
  if (!all(val == 1)) {
    stop("Input `panel` must be a balanced panel: it must have an observation for every unit at every time.")
  }

  panel = panel[order(panel[, unit], panel[, time]), ]
  num.years = length(unique(panel[, time]))
  num.units = length(unique(panel[, unit]))
  Y = matrix(panel[,outcome], num.units, num.years, byrow = TRUE,
             dimnames = list(unique(panel[,unit]), unique(panel[,time])))
  W = matrix(panel[,treatment], num.units, num.years, byrow = TRUE,
             dimnames = list(unique(panel[,unit]), unique(panel[,time])))
  w = apply(W, 1, any)                         # indicator for units that are treated at any time
  T0 = unname(which(apply(W, 2, any))[1]-1)    # last period nobody is treated
  N0 = sum(!w)

  if(! (all(W[!w,] == 0) && all(W[,1:T0] == 0) && all(W[w, (T0+1):ncol(Y)]==1))) {
    stop("The package cannot use this data. Treatment adoption is not simultaneous.")
  }

  unit.order = if(treated.last) { order(W[,T0+1], rownames(Y)) } else { 1:nrow(Y) }
  list(Y = Y[unit.order, ], N0 = N0, T0 = T0, W = W[unit.order, ])
}

```
#### Using synthetic controls 
(constructed with the help of : https://towardsdatascience.com/synthdid-101-a-beginners-guide-to-synthetic-difference-in-differences-84fed9b730ae)

```{r}
did_data_synth <- did_data[c("District", "year", "turnout_vage", "interaction")]
did_data_synth$turnout_vage <- did_data_synth$turnout_vage / 100
did_data_synth <- as.data.frame(as_tibble(did_data_synth))
matrix <- panel.matrices(did_data_synth, unit=1, time=2,
                          outcome=3, treatment=4)
synth_did <- synthdid_estimate(matrix$Y, matrix$N0, matrix$T0)
se <- sqrt(vcov(synth_did, method='jackknife'))
te_est <- sprintf('Point estimate for the treatment effect: %1.2f', synth_did)
CI <- sprintf('95%% CI (%1.2f, %1.2f)', synth_did - 1.96 * se, synth_did + 1.96 * se)
print(CI)
print(summary(synth_did))
table_synth <- xtable(synth_did)
print(table_synth)

```